\input{library}
\input{config}
\newcommand{\tab}{\hspace{\parindent}}
%-------------------------------------------------------------------------------
\begin{document}
\begin{titlepage}
\bordertitle
\begin{center}
\vspace{\fill} \maintitle \\ \vspace{\fill} \bottitle
\end{center}
\end{titlepage}
%-------------------------------------------------------------------------------
\newpage
\newgeometry{left=3cm,right=2cm,top=1cm,bottom=2cm}
\tableofcontents
\thispagestyle{empty}
%-------------------------------------------------------------------------------
\newpage
\chapter*{ Preface }
\thispagestyle{empty}
%-------------------------------------------------------------------------------
\vspace{\fill}
\begin{itemize}
\item 
\end{itemize}
\vspace{\fill}
%-------------------------------------------------------------------------------
\newpage
\setcounter{page}{1}
\chapter{ Introduction }
%-------------------------------------------------------------------------------
\section{Introduction and history}
    \textbf{Steganography} is the art of hidden writing, a term derived from
    Greek. It's the art and science of communicating in a way that conceals the
    very existence of the communication itself. The goal is to ensure that an
    outsider, or third party, doesn't realize that a secret message is being
    transmitted.
\section{Fundamental concepts}
    \textbf{Data hiding} is an overarching concept that refers to methods of
    concealing information within another medium. Its purpose is to protect
    information from unauthorized access and to maintain its confidentiality
    and integrity.\\
    
    \textbf{Steganography} and \textbf{watermarking} are two specialized
    sub-branches of data hiding, which differ primarily in their objectives.
\section{Differentiating techniques}
    \textbf{Steganography} aims to conceal the very existence of a message,
    prioritizing un-detectability. The system is considered to have failed if
    the message is discovered.\\
    
    In contrast, \textbf{digital watermarking} seeks to embed an identifying
    mark into data, prioritizing robustness. For the system to be successful,
    the watermark must survive attacks intended to remove or destroy it.\\
    
    \textbf{Cryptography} aims to protect the content of a message. It
    transforms readable text into an unreadable form (ciphertext), making it
    obvious that a message exists, but its meaning remains a secret.
\section{Introduction to techniques and applications}
    The following is a distinction of steganography methods based on the host
    medium:
    \begin{itemize}
        \item \textbf{Text Steganography:} Considered the most difficult due to
            the limited amount of redundant data available for embedding.
        \item \textbf{Image Steganography:} The most popular and widely
            researched method, as images provide a suitable medium for
            concealment.
        \item \textbf{Audio Steganography:} Involves embedding data into bits
            or frequencies that are imperceptible to the human ear.
        \item \textbf{Video Steganography:} Leverages the large data capacity
            of video by combining both image and audio steganography techniques.
        \item \textbf{Network Steganography:} Involves hiding information within
            network packets, often in fields like TCP/IP headers.
    \end{itemize}
\section{Basic Technique: LSB Substitution}
    \textbf{LSB substitution} (Least Significant Bit substitution) is a
    fundamental and widely-used steganography technique. It works by replacing
    the least significant bit (the last bit) of the bytes in a cover medium
    (like an image or audio file) with the bits of the secret message.\\
    
    This method is effective because the least significant bit has the smallest
    impact on the overall value of a byte. For example, in an image, changing
    the LSB of a pixel's color value results in a negligible color shift that is
    typically imperceptible to the humman eye.
    \subsection{How it works}
        Imagine a single pixel's red color value is represented by the byte
        \(11010010\). The LSB is the last \(0\). To embed a secret message bit,
        say a \(1\), you would simply replace the LSB, changing the byte to
        \(11010011\). This minor alteration is difficult for an observer to
        notice without specialized tools, effectively hiding the seret message.
    \subsection{Advantages and Disadvantages}
        It is simple to understand and easy to iplement. But it is not very
        robust. The hidden data can be easily destroyed by common operations
        like image compression or simple steganalysis attacks.
%-------------------------------------------------------------------------------
\chapter{Data hiding on image}
    To a computer, an image is a matrix of pixels. The three main types of
    images are:
    \begin{itemize}
        \item \textbf{Bitmap (Binary) Images:} each pixel is represented by a
            single bit (0 for white, 1 for black).
        \item \textbf{Grayscale Images:} Each pixel uses an 8-bit value to
            represent a range of black to white intensities.
        \item \textbf{RGB Images:} Each pixel is composed of three 8-bit color
            channels (Red, Green, Blue).
    \end{itemize}
    
    The most crucial component for steganography is the \textbf{data redundancy}
    within an image. Steganography leverages two key factors:
    \begin{itemize}
        \item \textbf{Redundant data:} insignificant bits whose alteration does
            not noticeably affect the image.
        \item \textbf{The imperceptibility of the human eye:} The human visual
            system cannot perceive very small changes in color.
    \end{itemize}
    
    Images with high detail are better suited for steganography because they
    contain more redundant data. Regarding file formats, \textbf{BMP}
    (uncompressed) files are large and can appear suspicious, whereas
    \textbf{JPEG} (compressed) is the most common format and is well-suited for
    modern steganography techniques.
\section{Spatial domain techniques and vulnerabilities}
    The \textbf{LSB} (Least Significant Bit) is the bit with the lowest weight,
    while the \textbf{MSB} (Most Significant Bit) is the bit with the highest
    weight. Changing the LSB of a pixel value creates a change that is virtually
    imperceptible to the human eye. For example, two colors with RGB values of
    (0,0,254) and (0,0,255) are nearly identical, demonstrating how a change in
    the least significant position has minimal visual impact.
    \subsection{LSB plane analysis}
        An 8-bit immage can be separated into eight bit planes. The \textbf{MSB}
        (Most Significant Bit) plane holds the main structure and overall visual
        information of the image. In contrast, the original \textbf{LSB}
        (Least Significant Bit) place of an image often looks like random noise.
        
        However, when a secret message is embedded using LSB steganography, it
        replaces this randomness with a more structured pattern. Therefore,
        extracting and analyzing the LSB plane can immediately reveal the
        presence of hidden data.
    \subsection{Steganalysis - Detection by Statistical Analysis}
        Steganalysis is the art and science of detecting the presence of a
        hidden message. While visually imperceptible, the act of \textbf{LSB
        substitution} alters the statistical properties of an image.
        Steganalytic tools are designed to analyze these subtle statistical
        changes, identifying anomalies that deviate from the expected
        distribution of a natural image, thereby revealing that data has been
        hidden within it.
    \subsection{Chi-Square attack}
        The idea is that in natural images, the frequency of adjacent pixel
        value pairs (e.g., 150 and 151) has a predictable relationship.
        \textbf{LSB embedding} disrupts this relationship, causing the
        frequencies of these pairs to become more equal.\\
        
        By measuring the difference between the observed frequency and the
        expected frequency, we can detect the presence of a hidden mmessage.
        A large difference in these values indicates a high probability that
        data has been embedded.
%-------------------------------------------------------------------------------
\chapter{Data hiding with deep learning and machine learning}
\chapter{Data hiding on video}
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
\end{document}
